---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BPrinStratTTE

<!-- badges: start -->
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Bayesian principal stratification for exponentially distributed time-to-event endpoints to explore potential immunogenicity effects in clinical trials of biologics.

## Scope

- The package contains functions to fit Bayesian principal stratification models and to perform clinical trial simulations in order to determine operating characteristics for given scenarios.
- Two-arm clinical trials of biologics are considered 
  - with an intercurrent event (determining the principal stratum of interest) that can only occur in the treated arm (such as the development of antidrug antibodies), and
  - with time-to-event endpoint that is assumed to follow an exponential distribution.
- Potential predictors of the intercurrent event can be taken into account.

## Installation

You can install the `BPrinStratTTE` package from GitHub with: 

```{r gh-installation, eval=F}
if (!require("remotes")) {install.packages("remotes")}
remotes::install_github("chstock/BPrinStratTTE")
```



