---
output: github_document
bibliography: "inst/references.bib"
csl: "inst/asa.csl"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BPrinStratTTE: Bayesian Principal Stratification for Time-to-Event Endpoints to Explore Immunogenicity Effects

<!-- badges: start -->
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Functions to fit Bayesian principal stratification models for time-to-event endpoints to explore immunogenicity effects in clinical trials of biological therapies.

## Scope

- The package contains functions to fit Bayesian principal stratification models and to perform clinical trial simulations to determine operating characteristics for given scenarios.
- Two-arm clinical trials of biological therapies are considered 
  - with an intercurrent event (determining the principal stratum of interest) that can only occur in the treated arm (such as the development of antidrug antibodies), and
  - with a time-to-event endpoint that is assumed to follow an exponential distribution.
- Effect estimators are hazard ratios and restricted mean survival times.
- Potential predictors of the intercurrent event can be taken into account.
- More flexible time-to-event distributions (piecewise-exponential and Weibull) will be considered in future versions of the package.


## Principal stratification methodology

- Principal stratification is an approach to estimate causal effects in partitions of subjects determined by post-treatment events. It was introduced in the biostatistical literature by @Frangakis2002.
- The ICH E9 (R1) addendum on estimands and sensitivity analysis in clinical trials proposed principal stratification as one approach to deal with intercurrent events in clinical trials (@ICHE9R1Guideline).
- For recent reviews of applications to clinical trials see @Lipkovich2022 and @Bornkamp2021. 
- Principal stratum membership is typically not known with certainty. A Bayesian approach may be particularly suited to deal with this type of uncertainty. Following a proposal by @Imbens1997, principal stratum membership can be treated as a latent mixture variable. 
- Motivated by scientific questions arising in clinical trials of biological therapies, in this package the approach by @Imbens1997 is adapted to a specific clinical trial setting with a time-to-event endpoint and the intercurrent event only occuring in the treated group. 

<!-- <font size="3"> -->
References: <br>
<div id="refs"></div>
<!-- </font> -->


## Installation

The `BPrinStratTTE` package can be installed from GitHub with: 

```{r gh-installation, eval=F}
if (!require("remotes")) {install.packages("remotes")}
remotes::install_github("Boehringer-Ingelheim/BPrinStratTTE")
```



